RSA + Scalar implicature / TBD

### 2015-11-28 models/RSA+AmbiguousSemantics.Rmd
entropy measures for scales

H.ge
H.ll
H.mu
H.sa
H.pd

>>>>

scales.entropy = data.frame(c("good_excellent",
                              "liked_loved",
                              "memorable_unforgettable",
                              "palatable_delicious",
                              "some_all"),
                            c(H.ge, H.ll, H.mu, H.pd, H.sa))
colnames(scales.entropy) = c("scale", "Entropy")

# Output to excel
# write.csv(scales.entropy, "model_data/scales_entorpy.csv", row.names=FALSE)
```
